Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-12-21 RegReport/paper_markup.tex
ready to submit final version

Stimuli were presented on a 17 inch CRT monitor with a resolution of $1024 \times 768$. Stimulus generation, presentation and data collection were controlled by Matlab and psychophysics toolbox \cite{brainard1997,cornelissen2002} run on a mac pro computer. The position of the right eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000Hz.

>>>>

\textcolor{red}{Most of the data was collected at the University of Aberdeen. Stimuli were presented on a 17 inch CRT monitor with a resolution of $1024 \times 768$. Around a third of participants were tested at the university using a 21 inch LCD panel with a resolution of $1920 \times 1080$. The display distance was set so that the visual angle of the stimuli was approximately the same between the two sites.} Stimulus generation, presentation and data collection were controlled by Matlab and psychophysics toolbox \cite{brainard1997,cornelissen2002} run on a mac pro computer. The position of the right eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000Hz.
